---
title: "Module 2 -  reveal js presentation"
author: "Prashant Dey"
date: "`r Sys.Date()`"
output: 
  revealjs::revealjs_presentation:
    transition: "zoom"
    background_transition: "concave"
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Code and Output

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

## Use a zoom transition {data-transition="zoom"}

## Fade in, Slide out {data-transition="slide-in fade-out"}

## Slide in, Fade out {data-transition="fade-in slide-out"}

## CSS color background {data-background=#ff0000}

## Full size image background {data-background="background.jpeg"}

## Video background {data-background-video="background.mp4"}

## A background page {data-background-iframe="https://example.com"}

